\sysfull

### 2018-04-17 paper/background.tex
background, methodology: TODOs in tables

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{|c|c|}
		\hline
		Model & Data Copied to/from NVRAM \\
		\hline\hline
		Mementos~\cite{mementos}	& Registers + Stack     \\
		DINO~\cite{dino}	& Registers + WAR variables \\
		Chain~\cite{chain}	& PC + channel data\\
		Alpaca~\cite{alpaca}	& PC + WAR variables \\
		Ratchet~\cite{ratchet}, Clank~\cite{hicks_isca_2017} & Registers (requires NV main memory) \\
		Region Formation~\cite{baghsorkhi_cgo_2018} & \textcolor{red}{XXX} \\
		\hline
	\end{tabular}
	\caption{Memory consistency enforcement overheads of intermittent execution models; \emph{PC}: program counter, \emph{channel data}: variables explicitly task-shared by the programmer, \emph{WAR variables}: variables involved in WAR dependences (\emph{NV}: non-volatile).}
	\label{table:chechpoint_comparison}
\end{table}

>>>>

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{|c|c|}
		\hline
		Model & Data Copied to/from NVRAM \\
		\hline\hline
		Mementos~\cite{mementos}	& Registers + Stack     \\
		DINO~\cite{dino}	& Registers + WAR variables \\
		Chain~\cite{chain}	& PC + channel data\\
		Alpaca~\cite{alpaca}	& PC + WAR variables \\
		Ratchet~\cite{ratchet}, Clank~\cite{hicks_isca_2017} & Registers (requires NV main memory) \\
		Region Formation~\cite{baghsorkhi_cgo_2018} & \textcolor{red}{XXX} \\
		\hline
	\end{tabular}
	\caption{Memory consistency enforcement overheads of intermittent execution models; \emph{PC}: program counter, \emph{channel data}: variables explicitly task-shared by the programmer, \emph{WAR variables}: variables involved in WAR dependences (\emph{NV}: non-volatile). \todo{region formation}{Alexei}}
	\label{table:chechpoint_comparison}
\end{table}

### 2018-04-17 paper/hwswsetup.tex
methodology: cite Intel paper on early state of LLVM MSP430 backend
background, methodology: TODOs in tables

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{| r|r|r | p{0.65\columnwidth} |}
		\hline
		Application & No. tasks & SLOC & Description \\
		\hline\hline
        \textbf{ar} & & & Activity recognition using a nearest neighbor
classifier with a deterministic input from a randomly-generated sequence of
accelerometer data\\
		\hline
        \textbf{bc} & & & Counts set bits in a pseudo-random sequence of bytes
using several algorithms and compares results for correctness\\
		\hline
        \textbf{cuckoo} & & & Inserts and queries a sequence of pseudo-random
values in a Cuckoo filter, a set membership data structure with deletion\\
		\hline
        \textbf{dijkstra} &  & & Dijkstra shortest path algorithm executed on a
predefined adjacency matrix\\
		\hline
        \textbf{fft} & & & Fast Fourier Transform on three pre-generated 128
sample vectors\\
		\hline
		\textbf{sort} & & & Selection sort of a fixed sequence of numbers\\
		\hline
	\end{tabular}
\caption{Description and characteristics of benchmark applications used to
evaluate \sys.}
\label{table:benchmark_table}
\end{table}

@@

Manual instrumentation of Alpaca code is not a general approach, but only
served as a practical alternative to porting the compiler pass from LLVM to
GCC.
%
Our experiments show that manually-instrumented Alpaca code compiled with GCC
is about 30\%-40\% faster than Alpaca code instrumented automatically by the
Alpaca LLVM compiler pass and compiled with LLVM. This performance difference is due to the early experimental state of the MSP430 backend for LLVM.
%
By compiling both systems with the same compiler (GCC), we ensure that our
comparison in Section~\ref{sec:evaluation} is fair.

>>>>

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{| r|r|r | p{0.65\columnwidth} |}
		\hline
		Application & No. tasks & SLOC & Description \\
		\hline\hline
        \textbf{ar} & & & Activity recognition using a nearest neighbor
classifier with a deterministic input from a randomly-generated sequence of
accelerometer data\\
		\hline
        \textbf{bc} & & & Counts set bits in a pseudo-random sequence of bytes
using several algorithms and compares results for correctness\\
		\hline
        \textbf{cuckoo} & & & Inserts and queries a sequence of pseudo-random
values in a Cuckoo filter, a set membership data structure with deletion\\
		\hline
        \textbf{dijkstra} &  & & Dijkstra shortest path algorithm executed on a
predefined adjacency matrix\\
		\hline
        \textbf{fft} & & & Fast Fourier Transform on three pre-generated 128
sample vectors\\
		\hline
		\textbf{sort} & & & Selection sort of a fixed sequence of numbers\\
		\hline
	\end{tabular}
\caption{Description and characteristics of benchmark applications used to
evaluate \sys. \todo{SLOC and Number of Tasks}{Amjad}}
\label{table:benchmark_table}
\end{table}

@@

Manual instrumentation of Alpaca code is not a general approach, but only
served as a practical alternative to porting the compiler pass from LLVM to
GCC.
%
Our experiments show that manually-instrumented Alpaca code compiled with GCC
is about 30\%-40\% faster than Alpaca code instrumented automatically by the
Alpaca LLVM compiler pass and compiled with LLVM. This performance difference
is due to the early experimental state of the MSP430 backend for
LLVM~\cite{baghsorkhi_cgo_2018}.
%
By compiling both systems with the same compiler (GCC), we ensure that our
comparison in Section~\ref{sec:evaluation} is fair.
